The problem and promise of scale in multilayer networks

### 2020-02-03 paper/manuscript.Rmd
clarify

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
(Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
temporal scale, we investigated the influence of the number of observations on
resulting multilayer networks. We randomly selected 500 timesteps and
iteratively included 25 additional observations, regenerating the multilayer
network and calculating associations of individuals. Subsequent iterations
included the previous set of observations to mimic observational data.

>>>>

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
(Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
temporal scale by adjusting the time window, we investigated the influence of the number of observations on
resulting multilayer networks. We randomly selected 500 timesteps and
iteratively included 25 additional observations, regenerating the multilayer
network and calculating associations of individuals. Subsequent iterations
included the previous set of observations to mimic observational data.
